Estimation of Intracortical Connectivity in a Dynamical Neural Field Model

### 2010-03-17 ltx/BrainIDE.tex
further updates to paper from meeting on 16/03/2010

	{Is this equation correct? Is it a convolution in time?}

@@

	{Do we really need this representation with $\bar t$. It makes convolution look wrong.}

@@

\begin{equation}\label{Connectivity Kernel}
	w\left(r,r'\right) = \theta^T \exp{\left(-\frac{\left(r_x - r_{x_n}\right)^2}{\left(2\sigma_w\right)^2}-\frac{\left(r_y - r_{y_n}\right)^2}{\left(2\sigma_w\right)^2}\right)}

@@

	\theta=\begin{bmatrix} \theta_{1}\\\theta_{2}\\\theta_{3}\end{bmatrix},\quad 		\sigma=\begin{bmatrix}\sigma_{m1}\\\sigma_{m2}\\ \sigma_{m3}\end{bmatrix}.

@@

	{Parham ... how are you writing this?}

@@

\section{Generating Data}
To generate iEEG/LFP data we proceeded with the assumption of spatial homogeneity for the connectivity and activation function parameters, implying $w(r,r') = w\left(|r-r'|\right)$, $\nu_0(r) = \nu_0$ and $v_0(r) = v_0$. In addition we assume the synaptic transmission delay is negligible such that $\bar{t}=t$. The model was discretized in time  (see Appendix~\ref{Time Discretization}) and a stochastic term was added to drive the system and account for uncertainty in the model giving
\begin{equation}\label{DiscreteTimeModel}
	v_{t+1}\left(r\right) = \lambda v_t\left(r\right) + \delta \int_\Omega { w\left(|r-r'|\right) f\left(v_t\left(r'\right)\right) dr'} + \delta I_t\left(r\right) + e_t\left(r\right)
\end{equation}
where $\delta$ is the time step, $\lambda = 1-\alpha\delta$ and $e_t(r) \sim \mathcal{GP}(0,\Sigma)$. The IDE formulation in Eq.~\ref{DiscreteTimeModel} was solved using a numerical method described in Appendix~\ref{Space Discretization}. To generate iEEG/LFP data we used the output function 
\begin{equation}
	y_t\left(r_n\right) = \int_{\Omega}{m\left(|r_n-r'|\right)v_t\left(r'\right)dr'}
\end{equation}
where $r_n$ defines the location of the sensors in the field where $n=1,...,N$ indexes the sensors. The output kernel $m(|r-r'|)$ governs the geometry of pick-up range of sensors where
\begin{equation}
	m\left(|r-r'|\right) = \exp{\left(-\frac{\left(r_x - r_{x_n}\right)^2}{\left(2\sigma_m\right)^2}-\frac{\left(r_y - r_{y_n}\right)^2}{\left(2\sigma_m\right)^2}\right)}.
\end{equation}

@@

\section{Spectral Analysis and Decomposition}

@@

\section{Numerical Solution to IDE Model}\label{Space Discretization}
To solve the convolution integral in \ref{Discrete Time Model1} we define the spatial aspect of the model on a regular square $i,j$ grid of neural masses, where the spatial step size $\Delta \mathbf{r}_i = \Delta \mathbf{r}_j = \Delta $ giving
\begin{equation}\label{discrete space}
	v_{t+1}\left(r_{ij}\right) =  \lambda v_t(r_{ij}) + \delta \Delta^2 \sum_{i=1}^{i=I}{\sum_{j=1}^{j=J}{\tilde{w}\left( |r_{ij}-r_{ij}'| \right)f\left( v_t\left( r_{ij}'\right) \right)} } + \delta I_t\left(r\right) + \tilde{e}_t(r_{i,j})
\end{equation}
where $\tilde{e}_t(r_{i,j}) \sim \mathcal{N}\left(0,\Sigma\right)$ and $\tilde{w}(|r_{ij}-r_{ij}'|)$ discretized connectivity kernel described by
\begin{equation}\label{Discrete Connectivity Kernel}
	\tilde{w}(r_{ij},r_{ij}') = \theta^T e^{\frac{\left(\left(r_i'-r_i\right)\Delta\right)^2}{(2\sigma)^2} + \frac{\left(\left(r_j'-r_j\right)\Delta\right)^2}{(2\sigma)^2}}.
\end{equation}
The observation equation and kernel were discretized in the same way by
\begin{equation}\label{Discrete Observation Equation}
    y_k\left(r_{i_n j_n}\right) = \Delta^2\sum_{i=1}^{i=I}\sum_{j=1}^{j=J} \tilde{m}( |r_{i_n j_n}-r_{ij}'| ) v_k\left(r_{ij}'\right)  + \varepsilon_k( r_{i_n j_n})
\end{equation}
where
\begin{equation}\label{Discrete Observation Kernel}
	\tilde{m}(|r_{ij}-r_{ij}'|) = e^{\frac{\left(\left(r_i'-r_i\right)\Delta\right)^2}{(2\sigma)^2} + \frac{\left(\left(r_j'-r_j\right)\Delta\right)^2}{(2\sigma)^2}}.
\end{equation}
We have used periodic boundary conditions to alleviate problems associated with edge effects.

>>>>

	{Is this equation correct? Is it a convolution in time? Dean: yes}

@@

	{Do we really need this representation with $\bar t$. It makes convolution look wrong. DF: Don't need since we dont include delays. The motivation was to be general at the beginning, and for everyone to understand how the model is used elsewhere.}

@@

\begin{eqnarray}\label{Connectivity Kernel}
	w\left(r,r'\right) &=& \theta^T \psi\left(r,r'\right) \\
	\psi\left(r,r'\right) &=&\exp{\left(-\frac{1}{2}(r'-r)^T\Sigma_w (r'-r)\right)}
\end{eqnarray}

@@

	\theta=\begin{bmatrix} \theta_{1}\\\theta_{2}\\\theta_{3}\end{bmatrix},\quad 		\Sigma_w=\begin{bmatrix}\Sigma_{w1}\\\Sigma_{w2}\\ \Sigma_{w3}\end{bmatrix}.

@@

	{Parham ... how are you writing this? DF: I have tried to make it better, but Parham can you check.}

@@

\section{Generating Data}
To generate iEEG/LFP data we proceeded with the assumption of spatial homogeneity for the connectivity and activation function parameters, implying $w(r,r') = w\left(|r-r'|\right)$, $\nu_0(r) = \nu_0$ and $v_0(r) = v_0$. In addition we assume the synaptic transmission delay is negligible such that $\bar{t}=t$. The model was discretized in time  (see Appendix~\ref{Time Discretization}) and a stochastic term was added to drive the system and account for uncertainty in the model giving
\begin{equation}\label{DiscreteTimeModel}
	v_{t+1}\left(r\right) = \lambda v_t\left(r\right) + \delta \int_\Omega { w\left(|r-r'|\right) f\left(v_t\left(r'\right)\right) dr'} + \delta I_t\left(r\right) + e_t\left(r\right)
\end{equation}
where $\delta$ is the time step, $\lambda = 1-\alpha\delta$ and $e_t(r) \sim \mathcal{GP}(0,\Sigma)$. The IDE formulation in Eq.~\ref{DiscreteTimeModel} was solved using a numerical method described in Appendix~\ref{Space Discretization}. To generate iEEG/LFP data we used the output function 
\begin{equation}
	y_t\left(r_n\right) = \int_{\Omega}{m\left(|r_n-r'|\right)v_t\left(r'\right)dr'}
\end{equation}
where $r_n$ defines the location of the sensors in the field where $n=1,...,N$ indexes the sensors. The output kernel $m(|r-r'|)$ governs the geometry of pick-up range of sensors where
\begin{equation}
	m\left(|r-r'|\right) = \exp{\left(-\frac{1}{2}(r'-r)^T\Sigma_m (r'-r)\right)}.
\end{equation}

@@

\section{Spectral Analysis and Decomposition}
This section provides

@@

\section{Numerical Solution to IDE Model}\label{Space Discretization}
To solve the intregro-difference equation in Eq.~\ref{Discrete Time Model1} we define the spatial aspect of the model on a regular square $i,j$ grid of neural masses, where the spatial step size $\Delta \mathbf{r}_i = \Delta \mathbf{r}_j = \Delta $ giving
\begin{equation}\label{discrete space}
	v_{t+1}\left(r_{ij}\right) =  \lambda v_t(r_{ij}) + \delta \Delta^2 \sum_{i=1}^{i=I}{\sum_{j=1}^{j=J}{\tilde{w}\left( |r_{ij}-r_{ij}'| \right)f\left( v_t\left( r_{ij}'\right) \right)} } + \delta I_t\left(r\right) + \tilde{e}_t(r_{i,j})
\end{equation}
where $\tilde{e}_t(r_{i,j}) \sim \mathcal{N}\left(0,\Sigma\right)$ and $\tilde{w}(|r_{ij}-r_{ij}'|)$ discretized connectivity kernel described by
\begin{equation}\label{Discrete Connectivity Kernel}
	\tilde{w}(r_{ij},r_{ij}') = \theta^T e^{\frac{\left(\left(r_i'-r_i\right)\Delta\right)^2}{(2\sigma)^2} + \frac{\left(\left(r_j'-r_j\right)\Delta\right)^2}{(2\sigma)^2}}.
\end{equation}
The observation equation and kernel were discretized in the same way by
\begin{equation}\label{Discrete Observation Equation}
    y_k\left(r_{i_n j_n}\right) = \Delta^2\sum_{i=1}^{i=I}\sum_{j=1}^{j=J} \tilde{m}( |r_{i_n j_n}-r_{ij}'| ) v_k\left(r_{ij}'\right)  + \varepsilon_k( r_{i_n j_n})
\end{equation}
where
\begin{equation}\label{Discrete Observation Kernel}
	\tilde{m}(|r_{ij}-r_{ij}'|) = e^{\frac{\left(\left(r_i'-r_i\right)\Delta\right)^2}{(2\sigma)^2} + \frac{\left(\left(r_j'-r_j\right)\Delta\right)^2}{(2\sigma)^2}}.
\end{equation}
We have used periodic boundary conditions to alleviate problems associated with edge effects.
